Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-29 doc/PRF2022/PRF_main.tex
yny

% body of paper here - Use proper section commands
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
interactions between JPs through the distribution of a hydrophobic potential (HAP). In a quiescent flow, numerical simulations of a 
JP suspension showed self-assembly into micelles and bilayers of JPs that provide an alternative means for computing the 
mechanical moduli of a colloidal membrane.

>>>>

% body of paper here - Use proper section commands
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids with two surfaces of different properties such as hydrophobicity. For example, it is common for the surface of a Janus particle to
be partly hydrophilic and hydrophobic (polar and non-polar). In a viscous solvent Janus particles often self-assemble into structures with tunable functions for biomedical engineering applications \cite{GheisariSahfieeAbbasiEtAl2021_DMR,LiuYangHuangEtAl2016_Angew,LiWangYaoEtAl2019_Nanoscale}. Depending on the interactions between Janus particles and the surrounding viscous solvent, JPs self-assemble into oligomers of various geometries and sizes.

{\bf The following paragraph needs to be rephrased and inserted in the introduction.
"Dynamics offers yet another dimension of control that emerges naturally from the interactions between particles and fluid in colloidal matter. ....Such active colloidal systems show nonequilibrium self-organization with complexity rivaling that of biological systems such as living cells, bacterial baths, and animal flocks.....long-standing challenges such as the ``inverse" problem of creating a colloidal system that will self-assemble into a prescribed structure.....the framework of geometrical frustration, which has been used to explain dis-ordered systems, could be used to design new ones instead, through specific choices for the shapes or interactions of the particles....\cite{Manoharan2015_Science}"}

The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
interactions between JPs through the distribution of a hydrophobic potential (HAP). In a quiescent flow, numerical simulations of a 
JP suspension showed self-assembly into micelles and bilayers of JPs that provide an alternative means for computing the 
mechanical moduli of a colloidal membrane.
